Data Preparation

### 2019-01-10 Data Preparation.Rmd
removing stopwords section
including d_manual to stemming section

d_description <- d_description %>%
  select(Code, `Calendar Year`, Description) %>%
  unnest_tokens(output = word, input = Description)
print(d_description_tidy)
```

@@

dictionary <- d_overview %>% 
  select(word) %>%
  distinct %>%
  arrange(word) %>%
  mutate(word_stem = purrr::map_chr(.x = word,
                                    .f = stem_hunspell))

# terms for which the stem differs from the original word
filter(dictionary, word != word_stem)
```

@@

```{r d_manual tidy}
d_manual <- unnest_tokens(d_manual, output = word, input = Manual)
```

>>>>

d_description <- d_description %>%
  select(Code, `Calendar Year`, Description) %>%
  unnest_tokens(output = word, input = Description)

d_manual <- unnest_tokens(d_manual, output = word, input = Manual)
```

@@

dictionary <- select(d_overview, Code, word) %>%
  rbind(d_manual) %>% 
  select(word) %>%
  distinct %>%
  mutate(word_stem = purrr::map_chr(.x = word,
                                    .f = stem_hunspell))

# terms for which the stem differs from the original word
filter(dictionary, word != word_stem)

@@

```{r d_manual tidy}
